Put Title here

### 2018-12-13 General WLD combinatorics.tex
Susama's changes

@@

\begin{proof}
Since the vertices of $\tau(W)$ are labeled by the edges of $W$, which are cyclically ordered, this gives an ordering to the vertices. Furthermore, since the outer polygon of $W$ is a cycle, the outer face of $\tau(W)$ is also a cycle. Since $W$ is admissible, no pairs of propagators cross. Therefore, it is a planar embedding. Similarly, $W$ does not admit any propagators of the form $p = (i, i+1)$; therefore there is exactly one edge connecting any two adjacent edges of $\tau(W)$. Finally, there does not exist two propagators $p,q$ such that both $p$ and $q$ start at edge $i$ and end at edge $j$. Therefore, no other two vertices of $\tau(W)$ can be connected by more than one edge. Finally, the embedding of $\tau(W)$ is induced from the embedding of the graph $W$.
 \end{proof}

@@

\begin{eg} \label{eg: unique decomposition} For the Wilson loop diagrams and polygon partitions in Example \ref{WLDtopolygonpartition}, the vertex sets $\{1, 2, 3,4\}$ and $\{5, 6, 7, 8\}$ give maximal triangulated pieces for both $\tau(W_1)$ and $\tau(W_3)$. The vertex set $\{4,5, 8, 1\}$ is not a triangulation in either polygon partition. \note{Put a picture of a dual tree.  Make a comment that the embedding is required to obtain uniqueness of the dual}
\end{eg}

@@

By \emph{splitting} a vertex $v$ we will mean replacing $v$ by new vertice $v_1, v_2,\ldots, v_{\text{deg}(v)}$ such that each $v_i$ as exactly one neighbour and the union of the neighbourhoods of the $v_i$ is the neighbourhood of $v$.

@@

>>>>

Note that this means that the set $F(\emptyset)$ is the maximal subset of vertices of $W$ of rank $0$. That is, it is the unique flat of rank $0$ in $M(W)$. \sanote{I'm sprinkling comments about $F(\emptyset)$ throughout until we can come up with a better name than unsupportive vertices.}

@@

\begin{proof}
Since the vertices of $\tau(W)$ are labeled by the edges of $W$, which are cyclically ordered, this gives an ordering to the vertices. Furthermore, since the outer \hlfix{circle of $W$ is a cycle}{sounds awkward in the new notation}, the outer face of $\tau(W)$ is also a cycle. Since $W$ is admissible, no pairs of propagators cross. Therefore, it is a planar embedding. Similarly, $W$ does not admit any propagators of the form $p = (i, i+1)$; therefore there is exactly one edge connecting any two adjacent edges of $\tau(W)$. Finally, there does not exist two propagators $p,q$ such that both $p$ and $q$ start at edge $i$ and end at edge $j$. Therefore, no other two vertices of $\tau(W)$ can be connected by more than one edge. Finally, the embedding of $\tau(W)$ is induced from the embedding of the graph $W$.
 \end{proof}

@@

\begin{eg} \label{eg: unique decomposition} For the Wilson loop diagrams and polygon partitions in Example \ref{WLDtopolygonpartition}, the vertex sets $\{1, 2, 3,4\}$ and $\{5, 6, 7, 8\}$ give maximal triangulated pieces for both $\tau(W_1)$ and $\tau(W_3)$. The vertex set $\{4,5, 8, 1\}$ is not a triangulation in either polygon partition. 
\end{eg}

@@

By \emph{splitting} a vertex $v$ we will mean replacing $v$ by new vertice $v_1, v_2,\ldots, v_{\text{deg}(v)}$ such that each $v_i$ has exactly one neighbour and the union of the \hlfix{neighbourhoods}{neigbors? Or a separate definition of neigborhood?} of the $v_i$ is the neighbourhood of $v$.

@@

\bas 
\begin{tikzpicture}[rotate=67.5,baseline=(current bounding box.east)]
	\begin{scope}
	\drawpolypart{8}{1.5}
    \drawnumbersshift
    \drawchord{1}{4}
    \drawchord{1}{3}
    \drawchord{5}{8}
    \drawchord{6}{8}
 \draw (0,0) node {$\bullet$};
\draw (-1,.2) node {$\bullet$};	
\draw (-.5,1.1) node {$\bullet$};
\draw (.8,-.3) node {$\bullet$};	
\draw (1.1,-.5) node {$\bullet$};
\draw(1.1,-.5) -- (.8,-.3) --(0,0)--(-1,.2) -- (-.5,1.1);
\foreach \i in {1,2,...,8} {
      \draw (45*\i:2) node {$\bullet$};
    }
\draw (45*1:2) --(0,0) -- (45*5:2);
\draw (45*6:2) -- (.8,-.3);
\draw (45*8:2) -- (1.1,-.5) -- (45*7:2);
\draw (45*2:2) -- (-.5,1.1) -- (45*3:2);
\draw (45*4:2) -- (-1,.2);
	\end{scope}
	\end{tikzpicture} \rightarrow 
\begin{tikzpicture}[rotate=67.5,baseline=(current bounding box.east)]
	\begin{scope}
	\drawpolypart{8}{1.5}
    \drawnumbersshift
    \drawchord{1}{4}
    \drawchord{1}{3}
    \drawchord{5}{8}
    \drawchord{6}{8}
 \draw (.1,.1) node {$\bullet$};
\draw (.1,-.1) node {$\bullet$};
\draw (-.1,-.1) node {$\bullet$};
\draw (-.1,.1) node {$\bullet$};
\draw (-1,.2) node {$\bullet$};	
\draw (-.5,1.1) node {$\bullet$};
\draw (.8,-.3) node {$\bullet$};	
\draw (1.1,-.5) node {$\bullet$};
\draw(1.1,-.5) -- (.8,-.3) --(.1,-.1); 
\draw (-.1, .1) --(-1,.2) -- (-.5,1.1);
\foreach \i in {1,2,...,8} {
      \draw (45*\i:2) node {$\bullet$};
    }
\draw (45*1:2) --(.1,.1);
\draw (-.1, -.1) -- (45*5:2);
\draw (45*6:2) -- (.8,-.3);
\draw (45*8:2) -- (1.1,-.5) -- (45*7:2);
\draw (45*2:2) -- (-.5,1.1) -- (45*3:2);
\draw (45*4:2) -- (-1,.2);
	\end{scope}
	\end{tikzpicture}
\eas
